SoK: Transparent Dishonesty. Front-running attacks on Blockchain.

### 2018-12-07 frontrunning/Latex/sections/paper.tex
[frontrunning] some edits + citations

Ethereum miners store pending transactions in pools and draw from them when forming blocks. As the term `pool' implies, there is no instinct order to how transactions are drawn from the pool and miners are free to sequence them arbitrarily.\footnote{Sometimes the pool is called a `queue.' It is important to note is a misnomer as queues use a first-in-first-out sequence.} This enables certain kinds of front-running, in particular transactions the miner will place before a pending transaction. A number of proposals attempt to thwart this attack by enforcing a rule about how to sequence transactions.

@@

An alternative is to sequence transactions psuedorandomly. This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) in Bitcoin cash which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}. Note that Bitcoin cash does not have a front-running problem for most standard transactions. While this could be used by Ethereum to make front-running statistically difficult, the protection is marginal at best and might even exacerbate attacks. A front-runner can construct multiple equivalent transactions, with slightly different values, until she finds a candidate that positions her transaction a desirable location in the resulting sequence. She broadcasts only this transaction and now miners that include her transaction will position it in front of transactions they heard about much earlier.

@@

%An implementation of fixed transaction ordering is Canonical Transaction Ordering Rule (CTOR) introduced in November 2018 fork of Bitcoin cash, which indicates an order in which blocks are valid based on the order of the transactions in them; coinbase first, then ascending lexicographic order based on transaction hash~\cite{bitcoinABC2018CTOR}. This solution can potentially mitigate the re-ordering attack by miners, however it does not prevent it fully. 
%NOTE: the two solutions above are both on the transaction ordering, however Silva's solution requires a logical timestamp, and CTOR uses sorting based on transaction hash.

@@

All transaction details in Bitcoin are make public and participant identities are only lightly protected. A number of techniques increase confidentiality [CT, bulletproofs] and anonymity [zerocoin, monero, etc] for cryptocurrencies. A current research direction is extending these protections to DApps. It is tempting to think that a confidential DApp would not permit front-running, as the front-runner would not know the details of the transaction she is front-running. However there are some nuances here to explore.

>>>>

Ethereum miners store pending transactions in pools and draw from them when forming blocks. As the term `pool' implies, there is no instinct order to how transactions are drawn from the pool and miners are free to sequence them arbitrarily.\footnote{Sometimes the pool is called a `queue.' It is important to note is a misnomer as queues use a first-in-first-out sequence.} This enables certain kinds of front-running, in particular transactions the miner will place before a pending transaction\footnote{The vanilla Go-Ethereum implementation, prioritizes transactions based on their gas price and nonce~\cite{EthMinerTxOrder}}. A number of proposals attempt to thwart this attack by enforcing a rule about how to sequence transactions.

@@

An alternative is to sequence transactions psuedorandomly. This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) by Bitcoin Cash ABC which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}. Note that Bitcoin does not have a front-running problem for most standard transactions. While this could be used by Ethereum to make front-running statistically difficult, the protection is marginal at best and might even exacerbate attacks. A front-runner can construct multiple equivalent transactions, with slightly different values, until she finds a candidate that positions her transaction a desirable location in the resulting sequence. She broadcasts only this transaction and now miners that include her transaction will position it in front of transactions they heard about much earlier.

@@

@@

All transaction details in Bitcoin are make public and participant identities are only lightly protected. A number of techniques increase confidentiality~\cite{bunzBulletproofs,maxwell2015confidential} and anonymity [zerocoin, monero, etc] for cryptocurrencies. A current research direction is extending these protections to DApps. It is tempting to think that a confidential DApp would not permit front-running, as the front-runner would not know the details of the transaction she is front-running. However there are some nuances here to explore.
